Hierarchical Reverberation Mapping

### 2013-08-31 Paper/ms.tex
Self references

There are deeper issues at play in reverberation mapping, that we will ignore
for the purposes of this letter. We list them here for completeness. Firstly,
the mean lag $\tau$ is not equal to $c$ times the mean radius of the BLR
distribution. Secondly, the mean lag $\tau$ is also not what the common
cross-correlation techniques measures, except in the case of very narrow
transfer functions.

@@

The prior for the underlying time variation of the continuum emission is
a continuous autoregressive process of order 1, or a CAR(1) model. These models
have been studied extensively for AGN variability
\citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.
Note that inferring $\bar{\tau}$ from the data requires that we
marginalise over an infinite number of nuisance parameters describing the
behaviour of $y(t)$ at unobserved times. This marginalisation can be done
either analytically or inside MCMC. We use the latter approach. We discretise
time using ten time bins per day, and have a discrete continuum light curve
$\mathbf{y} = \{y_1, ..., y_n\}$
\begin{eqnarray}
y_i = \mu + a\left(y_{i-1} - \mu\right) + \beta n_i
\end{eqnarray}
for $i \geq 2$, where the prior for the $\{n_i\}$ is independent standard
normal distributions. This is the discrete AR(1) model from time series theory.

@@

@@

>>>>

There are deeper issues at play in reverberation mapping, that we will ignore
for the purposes of this letter. We list them here for completeness. Firstly,
the mean lag $\tau$ is not equal to $c$ times the mean radius of the BLR
distribution. Secondly, the mean lag $\tau$ is also not what the common
cross-correlation techniques measures, except in the case of very narrow
transfer functions. Some of these difficulties have been addressed in other
contributions by \citet{pancoast} and \citet{arp151}.

@@

The prior for the underlying time variation of the continuum emission is
a continuous autoregressive process of order 1, or a CAR(1) model. These models
have been studied extensively for AGN variability
\citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.
Note that inferring $\bar{\tau}$ from the data requires that we
marginalise over an infinite number of nuisance parameters describing the
behaviour of $y(t)$ at unobserved times \citep{pancoast}.

This marginalisation can be done
either analytically or inside MCMC. We use the latter approach. We discretise
time using ten time bins per day, and have a discrete continuum light curve
$\mathbf{y} = \{y_1, ..., y_n\}$
\begin{eqnarray}
y_i = \mu + a\left(y_{i-1} - \mu\right) + \beta n_i
\end{eqnarray}
for $i \geq 2$, where the prior for the $\{n_i\}$ is independent standard
normal distributions. This is the discrete AR(1) model from time series theory.

@@

\bibitem[\protect\citeauthoryear{Brewer et al.}{2011}]{arp151} 
Brewer B.~J., et al., 2011, ApJ, 733, L33

@@

\bibitem[\protect\citeauthoryear{Pancoast, Brewer, 
\& Treu}{2011}]{pancoast} Pancoast A., Brewer B.~J., Treu T., 2011, ApJ, 730, 139
